Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-06-08 paper/manuscript.tex
Added methods and reference for unpassaged virus analyses.

>>>>

To determine the effect of virus passaging on the relationship between mutational effects and maximum frequencies in natural populations, we repeated the above analyses using only viruses that were sequenced directly without passaging.
Routine direct sequencing did not begin until the early 2000s \cite{McWhite2016}.
To construct a tree with a similar number of viruses as the original analysis, we sampled 30 viruses per month between January 1, 2000 and April 1, 2018, producing a tree with 2,374 unpassaged viruses with augur (commit: 6d9f708).
We included the passaged DMS strain, A/Perth/16/2009, in the resulting tree to enable comparison between pre-Perth and post-Perth clades.
